Verification of Stencil Computations with Spatial Specifications

### 2016-10-15 new-intro.tex
Emphesise that case studies are not synthetic
Fix typo in contributions

\item We give a detailed verification case study of two
  particular stencil computation, simulating programming errors.
  Our approach is able to detect the all possible
  indexing errors.
\end{itemize}
%

>>>>

\item We give a detailed verification case study of two
  particular stencil computation commonly used in scientifc computing,
  simulating programming errors. Our approach is able to detect all
  possible indexing errors for these computations.
\end{itemize}
%
